Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-01 W13report.tex
Fixed figures 14/15 and addressed AJC questions.

Detection on the difference image occurs through correlation of
$D(x,y)$ with the science image's PSF, yielding optimally filtered
detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v,x,y)$ where $\circ$
denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
maximum likelihood estimate of there being a point source at that
position.  Detection occurs by simply finding pixels that are more
than N sigma above the square root of the per--pixel variance.  
{XXX are you sure this is correlation - I thought it was convolution
  and should be cross_circ}

@@

After running an ensemble of 144 pipeline configurations, we
aggregated the numbers of false detections.  We report here the results for
each of the 3 visits, and for pre-- and postfiltering for
detection.  We cut on {\tt flags.pixel.edge} to remove spurious
detections on the immediate border of the image; other than that we do
no other cuts other than requiring that the {\tt centroid.sdss} is
finite.  We separated the {\tt DiaSources} that match with the reference
catalog (3'' matching radius) from those that don't (referred to as
orphans) to investigate the origins of the detections.  We found no
significant correlation of false detections with sensor within the
raft; therefore we report the aggregate results for all 9 sensors in
the analyses that follow.
{XXX is this true - Simon said it does vary from device to device}

@@

\section{Results: Correlation with KernelCandidate Statistics}

@@

\item For non-deconvolved image subtraction, prefiltering performs as
  well as post filtering in terms of the number of false positives.
{XXX true}

@@

\item The kernel is able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
  without a significant increase in the number of false positives.

@@

\begin{table}
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
\hline
Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
\hline
v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
\end{tabular}

\caption{Total number of false detections that we expect based on a
  4000x4072 pixel sensor.  This number is dependent on the seeing and
  detection threshold, so we list the values at a threshold of 4.5,
  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
  production. We list the total number of positive {\it plus} negative
  detections; they should be present in equal quantities. The variance
  is as determined from Monte Carlo simulations.\label{tab-fp} }
\end{table}

@@

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from
  detection and measurement, for the {\bf postfiltering} pipeline.
  Results for visit v6866601 are shown as {\it red squares}, for
  v6866602 as {\it green circles}, and for v6866603 {\it blue
    triangles}.  Three of the statistics, described in
  Section~\ref{sec-stats}, are presented.  They clearly correlate with
  each other.  For the deconvolution visit v6866601, the statistics
  are very poor even for the ``best'' solutions.  Points come from 
  all 144 production reductions of the same data, and detection at 5--sigma.
}
\label{corrpost}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from detection and
  measurement, for the {\bf prefiltering} pipeline.  Results for visit
  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
    circles}, and for v6866603 {\it blue triangles}.  Three of the
  statistics, described in Section~\ref{sec-stats}, are presented.
  They clearly correlate with each other, and also tend to correlate
  with the number of false detections (bottom row).}
\label{corrpre}
\end{figure}

>>>>

Detection on the difference image occurs through correlation of
$D(x,y)$ with the science image's PSF, yielding optimally filtered
detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v,x,y)$ where $\circ$
denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
maximum likelihood estimate of there being a point source at that
position.  Detection occurs by simply finding pixels that are more
than N sigma above the square root of the per--pixel variance.

@@

After running an ensemble of 144 pipeline configurations, we
aggregated the numbers of false detections.  We report here the results for
each of the 3 visits, and for pre-- and postfiltering for
detection.  We cut on {\tt flags.pixel.edge} to remove spurious
detections on the immediate border of the image; other than that we do
no other cuts other than requiring that the {\tt centroid.sdss} is
finite.  We separated the {\tt DiaSources} that match with the reference
catalog (3'' matching radius) from those that don't (referred to as
orphans) to investigate the origins of the detections.  We found no
significant correlation of false detections rate with sensor within the
raft (although the per--sensor optimal configs may be different, Section~\ref{sec-stats}); 
therefore we report the aggregate results for all 9 sensors in
the analyses that follow.

@@

\section{Results: Correlation with KernelCandidate Statistics \label{sec-stats}}

@@

\item For non--deconvolved image subtraction, prefiltering performs as
  well as postfiltering in terms of the number of false positives, when 
  corrected for the variance underestimate (Figure~\ref{fig-fp_v_thresh}).

@@

\item The kernel is able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
  without a significant increase in the number of false positives.  Because the prefiltering
  Gaussians tend to have larger sigmas, they are able to compensate for larger offsets.

@@

\begin{table}
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
\hline
Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
\hline
v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
\end{tabular}
\caption{Total number of false detections that we expect based on a
  4000x4072 pixel sensor.  This number is dependent on the seeing and
  detection threshold, so we list the values at a threshold of 4.5,
  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
  production. We list the total number of positive {\it plus} negative
  detections; they should be present in equal quantities. The variance
  is as determined from Monte Carlo simulations.\label{tab-fp} }
\end{table}

@@

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from
  detection and measurement, for the {\bf postfiltering} pipeline.
  Results for visit v6866601 are shown as {\it red squares}, for
  v6866602 as {\it green circles}, and for v6866603 {\it blue
    triangles}.  Three of the statistics, described in
  Section~\ref{sec-stats}, are presented.  They clearly correlate with
  each other.  For the deconvolution visit v6866601, the statistics
  are very poor even for the ``best'' solutions.  Points come from 
  all 144 production reductions of the same data, and detection at 5--sigma.
  The minimum numbers of 5--sigma false detections per--sensor (Table~\ref{tab-fp})
  are given by the horizontal lines.
}
\label{corrpost}
\end{figure}

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from detection and
  measurement, for the {\bf prefiltering} pipeline.  Results for visit
  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
    circles}, and for v6866603 {\it blue triangles}.  Three of the
  statistics, described in Section~\ref{sec-stats}, are presented.
  They clearly correlate with each other, and also tend to correlate
  with the number of false detections (bottom row).
  The minimum numbers of 5--sigma false detections per--sensor (Table~\ref{tab-fp})
  are given by the horizontal lines.
}
\label{corrpre}
\end{figure}
